The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-13 products/manuscript/Manuscript.qmd
Project Update

#  Verify Changes
glimpse(PROMO_Data)  # More readable than str()

#  Summary of Numeric Variables
print(skim(PROMO_Data))  # Explicitly print skim output

#  Frequency Counts of Key Categorical Variables
PROMO_Data %>% count(study_arm, sort = TRUE) %>% print()
PROMO_Data %>% count(placental_malaria, sort = TRUE) %>% print()
PROMO_Data %>% count(preterm_birth_ontoneo, sort = TRUE) %>% print()

@@

# Generate table only if dataset has rows
if (nrow(PROMO_Data) > 0) {
  baseline_characteristics <- PROMO_Data %>%
    select(all_of(baseline_vars)) %>%
    tbl_summary(by = study_arm) %>%
    add_p() %>%
    modify_header(label = "**Variable**") %>%
    bold_labels()

  # Display only the formatted table
  baseline_characteristics
} else {
  cat("️ No data available for analysis.")
}

@@

@@

  # Print the updated table
  print(malaria_outcomes_table)

} else {
  message("⚠️ No data available for analysis or insufficient variability in variables.")
}

>>>>

# Frequency counts of key categorical variables
# Store counts in variables without printing
study_arm_counts <- PROMO_Data %>% count(study_arm, sort = TRUE)
placental_malaria_counts <- PROMO_Data %>% count(placental_malaria, sort = TRUE)
preterm_birth_counts <- PROMO_Data %>% count(preterm_birth_ontoneo, sort = TRUE)

@@

# Generate table only if dataset has rows
if (nrow(PROMO_Data) > 0 && length(baseline_vars) > 1) {

  baseline_characteristics <- PROMO_Data %>%
    select(all_of(baseline_vars)) %>%
    tbl_summary(
      by = study_arm,
      statistic = list(all_categorical() ~ "{n} ({p}%)", all_continuous() ~ "{mean} ± {sd}")
    ) %>%
    add_p() %>%
    modify_header(label = "**Variable**") %>%
    bold_labels()

  # REMOVE print() → Directly output the table
  baseline_characteristics

} else {
  cat("⚠️ No data available for analysis.")
}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}

# Load required libraries
library(dplyr)
library(gtsummary)

@@

  # REMOVE print() → Just place the table here
  malaria_outcomes_table

} else {
  cat("⚠️ No data available for analysis or insufficient variability in variables.")
}
